Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-07-09 tensor/draft/draft-tensor-op.tex
[draft] corrections on introduction

\begin{abstract}
  The angular distribution of $B\to K\bar\ell\ell$ ($\ell =
  e,\,\mu,\,\tau$) provides a lepton-forward-backward asymmetry,
  $A_{\rm FB}^\ell$, and a flat term, $F_H^\ell$, that are strongly
  suppressed in the standard model. In both, nonstandard tensor and
  scalar contributions are enhanced with respect to vector ones. We
  use latest experimental results for $\ell = \mu$ in combination with
  $B_s\to \bar\mu\mu$ to derive stronger model-independent constraints
  on tensor and scalar effective couplings and determine their impact
  on not yet measured angular observables in $B\to K^*\bar\mu\mu$,
  which feature the same suppression of vector couplings.  Most
  notably, the measurement of $F_H^\mu$ provides constraints on
  (pseudo-)scalar couplings and their chirality-flipped counterparts
  that are complementary to the ones from the branching ratio $B_s\to
  \bar\mu\mu$, which allows to put for the first time simultaneously
  upper bounds on all four couplings. \fred{Try to shorten, add
    sentence ``independent of deviations in vector-coupling dominated
    observables''}
\end{abstract}

@@

With the first run of data taking by the LHCb Collaboration at the Large Hadron
Collider (LHC), $B$ physics has now also access to rather large samples of
rare $B$-meson decays with branching ratios below the $10^{-5}$. In consequence,
angular analyses of three- and four-body final states can be used to measure
a larger number of additional observables. Namely rare $B$ decays that are driven
at parton level by flavor-changing neutral current (FCNC) transitions $b\to s
\bar\ell\ell$ constitute valuable probes of the standard model (SM) and provide
constraints on its extensions, especially $B\to K^*(\to K\pi) \bar\ell\ell$, but
also $B\to K \bar\ell\ell$.

The angular distribution of $B\to K \bar\ell\ell$ in the angle $\theta_\ell$
between the $B$ and $\ell^-$ as measured in the dilepton rest frame
\begin{align}
  \label{eq:ang-distr}
  \frac{1}{\Gamma_\ell} \frac{\mbox{d}\Gamma_{\ell}}{\mbox{d}\!\cos\theta_\ell} &
  = \frac{3}{4} (1 - F_H^\ell) \sin^2\!\theta_\ell
  + \frac{1}{2} F_H^\ell
  + A_{\rm FB}^\ell \cos\theta_\ell \,,
\end{align}
normalised to the width $\Gamma_\ell$, has been recently updated with 3 fb$^{-1}$
by LHCb \cite{Aaij:2014tfa} for the mode $B^+\to K^+ \bar\mu\mu$, i.e. $\ell = \mu$,
with unprecedented precision, and the first analysis of $B^0\to K_{S} \bar\mu\mu$
has been reported as well. It provides the lepton-forward-backward asymmetry
$A_{\rm FB}^\mu$ and the flat term $F_H^\mu$ in CP-averaged form and integrated
over several bins in the dilepton invariant mass $q^2$. Similarly, the CP-averaged
branching ratios, ${\cal B}_\mu = \tau_{B} \Gamma_\mu$,~\cite{Aaij:2014pli}
and the rate CP asymmetry $A_{\rm CP}^\mu$ \cite{Aaij:2014bsa} are also
available from 3 fb$^{-1}$.

>>>>

\begin{abstract}
  The angular distribution of $B\to K\bar\ell\ell$ ($\ell =
  e,\,\mu,\,\tau$) provides a lepton-forward-backward asymmetry,
  $A_{\rm FB}^\ell$, and a flat term, $F_H^\ell$, that are strongly
  suppressed in the standard model. In both, nonstandard tensor and
  scalar contributions are enhanced with respect to vector ones. We
  use latest experimental results for $\ell = \mu$ in combination with
  $B_s\to \bar\mu\mu$ to derive stronger model-independent constraints
  on tensor and scalar effective couplings and determine their impact
  on not yet measured angular observables in $B\to K^*\bar\mu\mu$,
  which feature the same suppression of vector couplings.  Most
  notably, the measurement of $F_H^\mu$ provides constraints on
  (pseudo-)scalar couplings and their chirality-flipped counterparts
  that are complementary to the ones from the branching ratio $B_s\to
  \bar\mu\mu$, which allows to put for the first time simultaneously
  upper bounds on all four couplings. \fred{Try to shorten, add
    sentence ``independent of deviations in vector-coupling dominated
    observables''. There could be a bit of summary of outcome here, too}
\end{abstract}

@@

With the analysis of the data collected by the LHCb Collaboration
during phase I at the Large Hadron Collider (LHC), we now have access
to rather large samples of rare $B$ meson decays with branching ratios
below $10^{-5}$. As a consequence, angular analyses of three- and
four-body final states can be used to measure a larger number of
observables than previously possible at the B factories BaBar and
Belle. In this work we focus on rare $B$ decays driven at the parton
level by the flavor-changing neutral-current (FCNC) transition $b\to s
\bar\mu^+\mu^-$ that is well known to constitute a valuable probe of
the standard model (SM) and to provide constraints on its extensions
\fred{Here we need some references}.

The angular distribution of $B\to K \bar\ell\ell$---normalized to the
width $\Gamma_\ell$---in the angle $\theta_\ell$ between $B$ and
$\ell^-$ as measured in the dilepton rest frame is
\begin{align}
  \label{eq:ang-distr}
  \frac{1}{\Gamma_\ell} \frac{\mbox{d}\Gamma_{\ell}}{\mbox{d}\!\cos\theta_\ell} &
  = \frac{3}{4} (1 - F_H^\ell) \sin^2\!\theta_\ell
  + \frac{1}{2} F_H^\ell
  + A_{\rm FB}^\ell \cos\theta_\ell \,,
\end{align}
 has been recently updated with 3 fb$^{-1}$
by LHCb \cite{Aaij:2014tfa} for the mode $B^+\to K^+ \bar\mu\mu$, i.e. $\ell = \mu$,
with unprecedented precision, and the first analysis of $B^0\to K_{S} \bar\mu\mu$
has been reported as well. It provides the lepton-forward-backward asymmetry
$A_{\rm FB}^\mu$ and the flat term $F_H^\mu$ in CP-averaged form and integrated
over several bins in the dilepton invariant mass $q^2$. Similarly, the CP-averaged
branching ratios, ${\cal B}_\mu = \tau_{B} \Gamma_\mu$,~\cite{Aaij:2014pli}
and the rate CP asymmetry $A_{\rm CP}^\mu$ \cite{Aaij:2014bsa} are also
available from 3 fb$^{-1}$.
